---
title: "Prediction Assignment Wrtieup"
author: "Ishita Joshi"
date: "July 1, 2017"
output: html_document
---

## Summary

The goal of this project is to create a machine-learning algorithm that can correctly identify 
the quality of barbell bicep curls by using data from belt, forearm, arm, and dumbbell monitors. 
There are five classifications of this exercise, one method is the correct form of the exercise 
while the other four are common mistakes: exactly according to the specification (Class A), 
throwing the elbows to the front (Class B), lifting the dumbbell only halfway (Class C), 
lowering the dumbbell only halfway (Class D) and throwing the hips to the front (Class E).

## Data Cleaning

```{r}

##Data loading
setwd("~/Desktop/mydata/DS Coursera/Course -8 - Practical Machine Learning/coure project")
pmlTrain<-read.csv("pml-training.csv", header=T, na.strings=c("NA", "#DIV/0!"))
pmlTest<-read.csv("pml-testing.csv", header=T, na.string=c("NA", "#DIV/0!"))
```

```{r}
## NA exclusion for all available variables
noNApmlTrain<-pmlTrain[, apply(pmlTrain, 2, function(x) !any(is.na(x)))] 
dim(noNApmlTrain)
```

```{r}
cleanpmlTrain<-noNApmlTrain[,-c(1:8)]
dim(cleanpmlTrain)
```

```{r}
cleanpmltest<-pmlTest[,names(cleanpmlTrain[,-52])]
dim(cleanpmltest)
```

## Data Partitioning and Prediction Process

```{r}
library(caret)
inTrain<-createDataPartition(y=cleanpmlTrain$classe, p=0.75,list=F)
training<-cleanpmlTrain[inTrain,] 
test<-cleanpmlTrain[-inTrain,] 
#Training and test set dimensions
dim(training)
```

```{r}
dim(test)
```

##Conclusion

```{r}
library(caret)
set.seed(13333)
fitControl2<-trainControl(method="cv", number=5, allowParallel=T, verbose=T)
rffit<-train(classe~.,data=training, method="rf", trControl=fitControl2, verbose=F)
```

```{r}
predrf<-predict(rffit, newdata=test)
confusionMatrix(predrf, test$classe)
```

```{r}
pred20<-predict(rffit, newdata=cleanpmltest)
pred20
```

```{r}
fitControl2<-trainControl(method="cv", number=5, allowParallel=T, verbose=T)
gmbfit<-train(classe~.,data=training, method="gbm", trControl=fitControl2, verbose=F)
gmbfit$finalModel
class(gmbfit)
predgmb<-predict(gmbfit, newdata=test)
confusionMatrix(predgmb, test$classe)
predtrain<-predict(gmbfit, newdata=training)
confusionMatrix(predtrain, training$classe)
predtrain<-predict(gmbfit, newdata=training)
confusionMatrix(predtrain, training$classe)
```

```{r}
getwd()
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(pred20)
```